### 2019-09-20 proglog.tex
adds workshops and panels

\section{Program Logistics}

@@

\subsection{Panels}

>>>>

\section{Conference Program}

@@

\subsection{Saving the World Panel Series}
Technical and non-technical panels encourage interaction between students and professionals at the conference. Each panel is designed to address one or more of the stated goals for the conference. They also serve as a way for students and professionals to learn more about relevant issues, find inspiration for their next project, and feel encouraged for the future of the nuclear field.\\

$\Large\textbf{Technical Panels}$

\subsubsection{Critical Conversations: Microreactors}

\subsubsection{Applications for Fusion and Plasma}

\subsubsection{Nuclear Policy and Legislation}
Nuclear energy is one of the most heavily regulated fields in the United States. This panel aims to enlighten attendees about how legislation is written and how non-scientist government officials might better understand the potential of nuclear energy. This panel will allow attendees to learn who is working in this area and develop a network of people devoted to issues of nuclear policy.
Rita Baranwal would be an excellent speaker on this panel because of her work for the DOE.\\

$\Large\textbf{Non-Technical Panels}$

\subsubsection{Science is People: Conducting Inclusive Research}
Research and technology that will help us solve the grand challenge problems of the world must also reflect the diverse needs of the people that live in it. Everyone comes to nuclear engineering from a variety of backgrounds, identities, abilities, and experiences. Saving the World One Atom at a Time means making atomic contributions. Finding ways to encourage and include even one more person in the endeavor of nuclear science is an important kind of atomic contribution. This panel works toward the goal of celebrating the people behind the science. It also serves to inspire students and

\subsubsection{Talking To Non-Scientists}
It has been shown that when members of the general public are given more scientific evidence they are less likely to shift their beliefs. While this finding is surprising to members of the scientific community, people who value data and evidence, it can be difficult to find ways to effectively communicate your research to the public. Attendees will learn how other scientists effectively communicate their results. No longer discouraged by potential resistance from the public, students will steel their resolve for working on ambitious projects that can save the world. Suzanne Hobbs Baker would be a great choice for this panel, as well as members of The Story Collider; a non-profit organization devoted to helping scientists tell stories

\subsubsection{How to Host a Conference}

\subsection{Workshops}

\subsubsection{Scientific Storytelling}
Science is people. The Story Collider is a non-profit organization whose mission is to honor the people and stories behind the science and teach scientists to use these stories to their advantage. From their website:
\begin{quote}
	We know that storytelling is not typically taught during scientific training, and is sometimes explicitly discouraged. There are many reasons why. But like it or not, stories are how people understand the world, and they weave together fact and emotion. Compared to other forms of communication, these narratives can be more successful in:
	\begin{itemize}
		\item generating interest and engagement with a topic,
		\item improving comprehension, and
		\item influencing real-world beliefs, even among skeptical audiences.
	\end{itemize}
\end{quote}

### 2019-09-20 theme.tex
adds workshops and panels

\section{Saving the World One Atom at a Time}

The future is nuclear.\\
There are many challenges facing the world today and some have been designated existential threats to humanity. Young people today will witness the growing toll of anthropogenic climate change. As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming. We believe that many solutions will come from the nuclear sciences. The ANS student conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems. Whether the problem is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors. Our goal is to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems. Saving the world one atom at a time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems. This theme also honors the individual, atomic, contributions from students, researchers, and professionals, in the field of nuclear engineering, that are essential to progress. This conference is about science and it is about the people that make the science possible. Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference. We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.\\

>>>>

\section{Saving the World One Atom at a Time}
The future is nuclear.\\
There are many challenges facing the world today and some have been designated existential threats to humanity. Young people today will witness the growing toll of anthropogenic climate change. As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming. We believe that many solutions will come from the nuclear sciences. The ANS student conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems. Whether the problem is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors. Our goal is to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems. Saving the world one atom at a time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems. This theme also honors the individual, atomic, contributions from students, researchers, and professionals, in the field of nuclear engineering, that are essential to progress. This conference is about science and it is about the people that make the science possible. Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference. We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.\\
